---
title: "Working Through G. Grolemund & H. Wickhams’s [R for Data Science](http://r4ds.had.co.nz/index.html)"
author: "Krista DeStasio"
date: "7/11/2017"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
---

This R file walks through G. Grolemund & H. Wickhams’s online text, ["R for Data Science."](http://r4ds.had.co.nz/index.html) The code is commented so that the beginning R programmer can read through and understand what each line of code does and compare it to their own as they work through the text. Of course, there is more than one way to write code. This is only one sample way among many, and surely not the _most_ elegant.  

```{r setup, include=FALSE}
rm(list=ls()) # Clear the workspace
setwd("~/Dropbox/R_projects/R_practice/") # Set the working directory

## Install and load required packages
list.of.packages <- c("tidyverse", "knitr") # Make a character vector of packages used in the script
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])] # Which packages are not already installed
if(length(new.packages)) install.packages(new.packages) 
lapply(list.of.packages, library, character.only = TRUE) # If the list of packages we want and the list of new packages is not of the same length, install the packages listed in new.packages

knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/', echo=TRUE, warning=FALSE, message=FALSE) # Set the knit options: save figures to a folder, echo code chunks in the knitted document, don't print warnings in the knitted doc, don't print messages in the knitted doc.
```

# Chapter 3

Hypothesis: There is a negative linear relationship between engine size and fuel efficiency, such that as engine size increases fuel efficiency decreases.  

```{r Data visualization}
ggplot(data=mpg) + # specify data frame 
    geom_point(mapping = aes(x = displ, y = hwy)) # specify that plot is a scatterplot with displ on the x axis and hwy on the y axis
```

The plot confirms the hypothesis that there is a negative relationship between engine size and fuel efficiency.  
